Deep mutational scanning of hemagglutinin helps distinguish the evolutionary fates of human H3N2 influenza virus lineages

### 2018-01-19 paper/manuscript_origmethods.tex
Jesse a bit of work on Methods

\acknow{We thank Sarah Hilton, Hugh Haddox, and Sidney Bell for helpful discussions about data analysis. We thank the Fred Hutch Genomics Core for performing the Illumina deep sequencing. This work was supported by...}

>>>>

\acknow{We thank Sarah Hilton, Hugh Haddox, and Sidney Bell for helpful discussions about data analysis. 
We thank the Fred Hutch Genomics Core for performing the Illumina deep sequencing. 
This work was supported by grant R01AI127897 from the NIAID of the NIH. 
JML was supported in part by the Center for Inference and Dynamics of Infectious Diseases (CIDID), which is funded by grant U54GM111274 from the NIGMS of the NIH.
The research of JDB is supported in part by a Faculty Scholar grant from the Howard Hughes Medical Institute and the Simons Foundation, and a Burroughs Wellcome Young Investigator in the Pathogenesis of Infectious Diseases grant.
\comment{Add any additional relevant grants for Trevor and John}
}
